Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Update pictures to account for log10 video games moving to categorical graph.

<<VisReasoningAnalysis,echo=FALSE, include=FALSE, fig.width=10,fig.height=5, out.width='\\linewidth'>>=
lineup.summary$variable <- factor(lineup.summary$variable, labels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search", "Log10 Video Game Hrs/Wk"))
lineup.summary$variable <- factor(lineup.summary$variable, levels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search", "Log10 Video Game Hrs/Wk"))

qplot(data=lineup.summary, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x", ncol=3) + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + geom_smooth(method="lm") + theme_bw()
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCts.png", sep=""), width=6, height=4)

lineup.summary.categorical <- rbind(lineup.summary.categorical, data.frame(id=1, lineup=NA, variable="verbal_skills", value=1))
lineup.summary.categorical <- rbind(lineup.summary.categorical, data.frame(id=1, lineup=NA, variable="math_skills", value=1))
lineup.summary.categorical$variable <- factor(lineup.summary.categorical$variable, labels=c("Age", "Sex", "Math/Science Research", "Statistics Class", "Calculus 1", "Verbal Skills", "Math Skills", "Art Skills", "AutoCAD Experience"))
lineup.summary.categorical$value[lineup.summary.categorical$value=="f"] <- "Female"
lineup.summary.categorical$value[lineup.summary.categorical$value=="m"] <- "Male"
lineup.summary.categorical$value[lineup.summary.categorical$value=="y"] <- "TRUE"
lineup.summary.categorical$value[lineup.summary.categorical$value=="n"] <- "FALSE"

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x", ncol=3) + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=6, height=6)
@

>>>>

<<VisReasoningAnalysis,echo=FALSE, include=FALSE, fig.width=10,fig.height=5, out.width='\\linewidth'>>=
lineup.summary$variable <- factor(lineup.summary$variable, labels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search"))

qplot(data=lineup.summary, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x") + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + geom_smooth(method="lm") + theme_bw()
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCts.png", sep=""), width=6, height=4)

lineup.summary.categorical <- rbind(lineup.summary.categorical, data.frame(id=1, lineup=NA, variable="verbal_skills", value=1))
lineup.summary.categorical <- rbind(lineup.summary.categorical, data.frame(id=1, lineup=NA, variable="math_skills", value=1))
lineup.summary.categorical$variable <- factor(lineup.summary.categorical$variable, labels=c("Age", "Sex", "Math/Science Research", "Statistics Class", "Calculus 1", "Verbal Skills", "Math Skills", "Art Skills", "AutoCAD Experience", "Log10 Video Game Hours"))
lineup.summary.categorical$value[lineup.summary.categorical$value=="f"] <- "Female"
lineup.summary.categorical$value[lineup.summary.categorical$value=="m"] <- "Male"
lineup.summary.categorical$value[lineup.summary.categorical$value=="y"] <- "TRUE"
lineup.summary.categorical$value[lineup.summary.categorical$value=="n"] <- "FALSE"

qplot(data=subset(lineup.summary.categorical, variable!="Log10 Video Game Hours"), x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x", ncol=3) + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=6, height=6)
@
